tl20-05_berghei_pir_GeneSetEnrichmentQusage

### 2021-09-16 chapter3_results_bergheiPir/Manuscript_berghei_pir_GeneSetEnrichmentQusage.Rmd
Save pirvnonpir TPM comparison graph

all_stats_df_cast <- all_stats_df_cast[ordering(rownames(all_stats_df_cast),
                                                r_order_vector),
                                       order_path.names]

Heatmap(all_stats_df_cast,
        name = 'logFoldChange',
        cluster_rows = FALSE,
        cluster_columns = FALSE,
        rect_gp = gpar(col = "white", lwd = 2),
        cell_fun = function(j, i, x, y, width, height, fill){
          fdr_val <- all_stats_df[
            all_stats_df$contrast == rownames(all_stats_df_cast[i,]),
          ]$fdr_r[j]
          if(fdr_val<= 0.05){
            grid.text(
              sprintf("%.3f", #One significant figure
                      fdr_val),
              x,
              y,
              gp = gpar(fontsize = 10,
                        fontface = 'bold')
            )
          }
        })
```

>>>>

all_stats_df_cast <- all_stats_df_cast[ordering(rownames(all_stats_df_cast),
                                                r_order_vector),
                                       order_path.names]
png(filename = "plots/thesis_chapter3_figure_statsCompHeatmap_geneGroups.png",
    width = 7,
    height = 5,
    units = "in",
    res = 330)
Heatmap(all_stats_df_cast,
        name = 'logFoldChange',
        cluster_rows = FALSE,
        cluster_columns = FALSE,
        rect_gp = gpar(col = "white", lwd = 2),
        cell_fun = function(j, i, x, y, width, height, fill){
          fdr_val <- all_stats_df[
            all_stats_df$contrast == rownames(all_stats_df_cast[i,]),
          ]$fdr_r[j]
          if(fdr_val<= 0.05){
            grid.text(
              sprintf("%.3f", #One significant figure
                      fdr_val),
              x,
              y,
              gp = gpar(fontsize = 10,
                        fontface = 'bold')
            )
          }
        })
dev.off()
```
